Software Citation Principles

### 2016-07-30 sc-principles/rebuttal/rebuttal.tex

\item \textbf{Reviewer comment:}
\emph{I find it a bit weird to quote passages from the same paper like ``The Accessibility principle (5) states that ?....?'' (line 329 and others).}

\textbf{Our response:}
We feel it is more clear to a reader to quote the basis by which we are making follow-on comments, rather than just pointing back to a previous part of the paper.

\item \textbf{Reviewer comment:}
\emph{In the discussion about Unique identification (lines 292+), I miss the discussion of hash values as version identifiers, as applied by Git for instance. As the first author is affiliated with GitHub, I assume this aspect was left out intentionally, but why? As basically all software is nowadays maintained with version control systems such as Git, these identifiers come for free and are by design unique. So, I would think they are an important aspect to discuss for software citations.}

\textbf{Our response:}
While we agree there is value in including the explicit version (e.g., Git SHA1 hash, Subversion revision number) of the software in a software citation, we also believe there are a number of reasons that this, by itself, is not sufficient for the purposes of software citation:

\begin{itemize}
\item Version numbers are not guaranteed to be permanent: projects can be migrated to new version control systems (e.g., SVN to Git). In addition, it is possible to overwrite versions (e.g., Git force-pushing).
\item Stating a version number doesn't guarantee that the software is available at a particular (web-resolvable) URL.
\item When we talk about a ``Unique identifier'' in the document, we are referring to unique, persistent, and machine-actionable identifiers such as a DOI, ARK, or PURL; we do not believe a repository address with a version number is sufficient.
\end{itemize}

We recommend that software citations capture the versions of the code expressed as (ideally) a semantic version (SemVer) number (\url{http://semver.org/}). These are points in time at which the authors of the code made the explicit decision to release the code.
We feel a SemVer release number together with a DOI (and associated archive in, e.g., Zenodo) is the most robust and future-proof solution. That said, in the absence of ``recommended'' identifiers (such as a DOI) a Git SHA together with a link to a Git repository would be preferable to not having this information.

### 2016-07-30 sc-principles/software-citation-principles.tex
spelling fix
final minor edits

Some of the most actionable work has come from the UK Software Sustainability
Institute (SSI) in the form of blog posts written by their community fellows.
For examplel, in a blog post from 2012, Jackson discusses some of the pitfalls
of trying to cite software in publications~\cite{ssi-how-to-cite}. He includes
useful guidance for when to consider citing software as well as some ways to help
``convince'' journal editors to allow the inclusion of software citations.

@@

While we believe there is value in including the explicit version (e.g., Git SHA1 hash, Subversion revision number) of the software in any software citation, we believe there are a number of reasons that a commit reference together with a repository URL is not ideal for the purposes of software citation:

\begin{enumerate}
\item Version numbers/commit references are not guaranteed to be permanent. Projects can be migrated to new version control systems (e.g., SVN to Git). In addition, it is possible to overwrite/clobber particular version (e.g., force-pushing in the case of Git).
\item A repository address and version number doesn't guarantee that the software is available at a particular (resolvable) URL.
\item A particular version number/commit reference may not represent a `preferred' point at which to cite the software from the perspective of the package authors.
\end{enumerate}

Note that the ``unique'' in a UID means that it points to a unique, specific software. However, multiple UIDs might point to the same software.
This is not recommended, but is possible.
\textit{We strongly recommend that if there is already a UID for a version of software, no additional UID should be created.}
Multiple UIDs can lead to split credit, which goes against the Credit and Attribution principle (\ref{principle:credit}).

>>>>

Some of the most actionable work has come from the UK Software Sustainability
Institute (SSI) in the form of blog posts written by their community fellows.
For example, in a blog post from 2012, Jackson discusses some of the pitfalls
of trying to cite software in publications~\cite{ssi-how-to-cite}. He includes
useful guidance for when to consider citing software as well as some ways to help
``convince'' journal editors to allow the inclusion of software citations.

@@

While we believe there is value in including the explicit version (e.g., Git SHA1 hash, Subversion revision number) of the software in any software citation, there are a number of reasons that a commit reference together with a repository URL is not ideal for the purposes of software citation:

\begin{enumerate}
\item Version numbers/commit references are not guaranteed to be permanent. Projects can be migrated to new version control systems (e.g., SVN to Git). In addition, it is possible to overwrite/clobber a particular version (e.g., force-pushing in the case of Git).
\item A repository address and version number does not guarantee that the software is available at a particular (resolvable) URL.
\item A particular version number/commit reference may not represent a ``preferred'' point at which to cite the software from the perspective of the package authors.
\end{enumerate}

Note that the ``unique'' in a UID means that it points to a unique, specific software version. However, multiple UIDs might point to the same software.
This is not recommended, but is possible.
\textit{We strongly recommend that if there is already a UID for a version of software, no additional UID should be created.}
Multiple UIDs can lead to split credit, which goes against the Credit and Attribution principle (\ref{principle:credit}).
